---
title: "Beer Data"
author: "Alex Salamah"
date: "App last updated on: 11/13/2019"
output: html_document
runtime: shiny
---
<style type="text/css">

h1.title {
  font-size: 38px;
  color: Blue;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Blue;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: Blue;
  text-align: center;


#header 
    background: #2274cc; /* Old browsers */
    background: -moz-linear-gradient(left, #2274cc 0%, #26c5d3 36%, #61bf61 100%); /* FF3.6-15 */
    background: -webkit-linear-gradient(left, #2274cc 0%,#26c5d3 36%,#61bf61 100%); /* Chrome10-25,Safari5.1-6 */
    background: linear-gradient(to right, #2274cc 0%,#26c5d3 36%,#61bf61 100%); /* W3C, IE10+, FF16+, Chrome26+,  Opera12+, Safari7+ */
    filter: progid:DXImageTransform.Microsoft.gradient( startColorstr='#2274cc', endColorstr='#61bf61',GradientType=1 ); /* IE6-9 */
    color: white;
    height: 100px;
    display:flex;
    align-items: center;
    justify-content: center;
  }
</style>
<br>
<br>

```{r, include=FALSE}
# Get the data
# Adding setwd() would result in error when publishing to Shiny!
BeersDF <- read.csv(file = "Beers.csv", header = TRUE)
BreweriesDF <- read.csv(file = "Breweries.csv", header = TRUE)
AlcoholDF <- read.csv(file = "AlcoholAbuse.csv", header = TRUE)
```

```{r, include=FALSE}
# Visualization
library(tidyverse)
library(plotly)
library(plyr)
library(dplyr)
library(maps)
library(inspectdf)
library(VIM)
library(ggthemes)
library(GGally)
library(prettydoc)
library(treemap)
library(gridExtra)

# data wrangling 
library(stringr)
library(tm)
library(knitr)
library(sqldf)
library(dataMaid)

# classification and modeling
library(class)
library(e1071)
library(caret)
```

```{r include=FALSE}
## 2. Merge beer data with the breweries data.
mergeDF <- merge(BeersDF, BreweriesDF, by.x = "Brewery_id", by.y = "Brew_ID")
colnames(mergeDF)[2] = "Beer_name"
colnames(mergeDF)[8] = "Brewery_name"
```

```{r include=FALSE}
## 3. Address the missing values in each column.  
matrixplot(mergeDF)
marginplot(mergeDF[c("ABV","IBU")], pch = c(20), col = c("darkgray", "red", "blue"))
IBUNADF <-  mergeDF %>% filter(is.na(IBU))
ABVNADF <-  mergeDF %>% filter(is.na(ABV))
BOTHNADF <- mergeDF %>% filter(is.na(ABV) & is.na(IBU))
# Calculate IBU and ABV median value of each state
IBUmedianState <- mergeDF %>% filter(!is.na(IBU)) %>% group_by(State) %>% dplyr::summarise(IBUmedian=median(IBU))
ABVmedianState <- mergeDF %>% filter(!is.na(ABV)) %>% group_by(State) %>% dplyr::summarise(ABVmedian=median(ABV))
# Replace IBU NA's with state median value
mergeDF_no_IBU_NA <- left_join(mergeDF, IBUmedianState, by = "State")
mergeDF_no_IBU_NA$IBU[is.na(mergeDF_no_IBU_NA$IBU)]  <- as.character(mergeDF_no_IBU_NA$IBUmedian[is.na(mergeDF_no_IBU_NA$IBU)])
# Replace 7 IBU NA's in SD with grand median value 35.00
mergeDF_no_IBU_NA$IBU = str_replace_na(mergeDF_no_IBU_NA$IBU, replacement =  "35")
mergeDF_no_IBU_NA$IBUmedian = str_replace_na(mergeDF_no_IBU_NA$IBUmedian, replacement =  "35")
# Replace ABV NA's with state median value
mergeDF_noNA <- left_join(mergeDF_no_IBU_NA, ABVmedianState, by = "State")
mergeDF_noNA$ABV[is.na(mergeDF_noNA$ABV)] <- as.character(mergeDF_noNA$ABVmedian[is.na(mergeDF_noNA$ABV)])
mergeDF_noNA$IBU <- as.numeric(mergeDF_noNA$IBU)
mergeDF_noNA$ABV <- as.numeric(mergeDF_noNA$ABV)

```

```{r echo=FALSE}
# youtube: https://www.youtube.com/watch?v=AFau9WJbZj4
library(shiny)
#library(reshape2)

ui <- fluidPage(
 # titlePanel("US Craft Beer Data"),
  
  # Application title
  sidebarLayout(
    sidebarPanel(
      # Select state
      selectInput("inState", "Select state to show plot", choices = mergeDF_noNA$State),
      
      # Select plots
      selectInput("select", "Select plot type", choices = c("Histogram", "Boxplot", "Scatterplot", "Correlation")),
      
      # Select regression line in scatterplot
      selectInput("selectline", "Add a regression line?", choices = c("Yes", "No"))
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
      tabsetPanel(
        tabPanel("Plot",
                 fluidRow(
                   splitLayout(cellWidths = "400px",
                                 #c("50%", "50%"),
                   plotOutput("distPlot1", height = "300px", width = "450px"),
                   plotOutput("distPlot2", height = "300px", width = "450px"),
                   column(width = 10)
                                      #,
                   #plotOutput("distPlot3"),
                   #plotOutput("distPlot4")
                   )
        )),
      
      tabPanel("Raw Data", tableOutput("BeerData"))
   )
  )
)
)

# Taking the 'input' from UI, giving the 'output' back to UI.
# renderTable is a reactive function, which means that whenever user is changing any value, the table value is getting changed.
server <- function(input, output) {
  
  # Output Beer data table
  output$BeerData <- renderTable({
    stateFilter <- subset(mergeDF_noNA, mergeDF_noNA$State == input$inState)
  })
  
  # output Beer plots
    output$distPlot1 <- renderPlot({
      stateFilter <- subset(mergeDF_noNA, mergeDF_noNA$State == input$inState)
      if(input$select == "Histogram")
        {
        stateFilter %>% ggplot(aes(x=ABV)) + geom_histogram(fill="blue", color="white") + ggtitle("Histogram ABV")
      }
      else
        if(input$select == "Boxplot")
          {
          stateFilter %>% ggplot(aes(y=ABV, fill=as.factor(Ounces))) + geom_boxplot() +
            xlab("Ale Types (IPA or ALE)") + ylab("ABV") + ggtitle("Boxplot of ABV vs Ale Type")
        }
      else
        if(input$select == "Scatterplot")
        {
          if(input$selectline == "Yes")
          {
            p1 <- stateFilter %>% ggplot(aes(x=ABV, y=IBU)) + geom_point(aes(color=State), size=1, position="jitter") +
              geom_smooth(method = lm) + ggtitle("Scatterplot: IBU vs ABV with regression line")
            grid.arrange(p1, ncol=1, widths = c(4))
          }
          else
            if(input$selectline == "No")
            {
              stateFilter %>% ggplot(aes(x=ABV, y=IBU)) + geom_point(aes(color=State), size=1, position="jitter") +
                ggtitle("Scatterplot: IBU vs ABV no regression line")                    
            }
        }
      else
        if(input$select == "Correlation")
        {
#          Brew_Name.notna <- BreweriesDF %>% filter(!is.na(Name)) # 558 not NA
Corl <- inspect_cor(BeersDF)
show_plot (Corl, plot_layout = c(3, 5))
 
           # Brew_tm1 <- Brew_Name.notna %>% group_by(State) %>%  dplyr::summarise(NumBrew=n())
           # Brew_tm1$State.NumBrew <- do.call(paste, c(Brew_tm1[c("State","NumBrew")], sep = "\n")) 
           # 
           # treemap(Brew_tm1, # Your data frame object
           #         index = c("State.NumBrew"),
           #         vSize = "NumBrew",
           #         type = "index", # index, value, comp, dens, depth, categorical, color, manual
           #         palette = "Reds",
           #         title = "Number of Breweries in States",
           #         fontsize.title = 14
           #         )
        }
      })
    
    output$distPlot2 <- renderPlot({
      stateFilter <- subset(mergeDF_noNA, mergeDF_noNA$State == input$inState)
      if(input$select == "Histogram")
        {
        stateFilter %>% ggplot(aes(x=IBU)) + geom_histogram(fill="orange", color="black") + ggtitle("Histogram IBU")
      }
      else
        if(input$select == "Boxplot")
          {
          stateFilter %>% ggplot(aes(y=IBU, fill=as.factor(Ounces))) + geom_boxplot() +
            xlab("Ale Types (IPA or ALE)") + ylab("IBU") + ggtitle("Boxplot of IBU vs Ale Type")
        }
    })
  }

shinyApp(ui, server)
```

